---
title: "Pilot Data"
author: Spencer Weston, Carlos Moreno, Anand Patel, Alexandra Drossos, and Madeline
  Whitlow
date: "11/2/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars, echo=FALSE, include=FALSE}
library(data.table)
library(ggplot2)
source('./src/data_pathes.R')
interim_folder <- interim_data_folder()
data_path <- file.path(interim_folder, 'simple_assignment_response_match.csv')
d <- fread(data_path)
```

## Pilot Data

We have received 36 responses as of 11/1/2021. We began collecting data on 10/31/2021
and will accept responses up until 11/14/2021. Of these 36 responses, 10 could not 
be trivially attributed to a subject due to a difference between the email we assigned
to treatment and the email we received a response from. We expect that we will be 
able to match these responses to their treatment group in time.

For now, we present a histogram of responses by treatment group for the matched subjects. Our control group
provides no monetary reward for completing the survey. We have two treatment groups.
The first offers a guaranteed $5 Amazon gift card for completing the survey. The second offers entry
into a lottery for a $100 Amazon gift card.

```{r, echo=FALSE}
hist_data <- d[, .N, by=treatment_group]
hist_data[, group := ifelse(treatment_group==0, 'control', ifelse(treatment_group == 1, '$5 guaranteed', "$100 lottery"))] 
ggplot(data=hist_data, aes(x=group, y=N)) + geom_col() +
  ggtitle("Number of Responses by Treatment Group", subtitle= "N=26") +
  xlab("Treatment Group") + ylab("Number of Responses")

```

