---
title: "w241_final_matching"
author: "CEM"
date: "11/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='hide', message=FALSE, warning=FALSE}
library(data.table)                     # for data manipulation 
library(sandwich)                       # for creating robust SEs 
library(lmtest)                         # for easy testing with robuse SEs
library(stargazer)                      # for printing tables 
library(ggplot2)
library(tidyverse)

#library(grid)
#library(gridExtra)
library(cowplot)
library(plyr)
```

```{r}
#Function to calculate the Robust SE
robust_SE <- function(model){
  return(sqrt(diag(vcovHC(model))) )
}
```


```{r}
df1 <- read.csv("../Final_Matching_Test/treatment_assignment.csv")
dfr <- read.csv("../Final_Matching_Test/assignment_response_match.csv")
answers <- dfr$full_name
df1 <- data.table(df1)
df1[ , response := ifelse(full_name %in% answers, 1, 0)]
head(df1)
```
```{r}
write.csv(df1,"consolidated_response_rate.csv")
```


```{r Read in consolidated response rate}
df1 <- read.csv("consolidated_response_rate.csv")
df1 <- data.table(df1)
```


### Renaming Variables and Values

```{r}
df1[ , treatment_group_name := ifelse(treatment_group == 0, "No Incentive (Control)", 
                                      ifelse(treatment_group == 1, "$5 Incentive", "$100 Lottery"))]

df1[ , .(count = .N), by=.(treatment_group_name)]
```


```{r}
df1[ , cohort_name := mapvalues(df1$cohort, 
                                from = c(0, 1, 2, 3, 4), 
                                to = c("Summer 2020", "Fall 2020", "Spring 2021", "Summer 2021", "Fall 2021"))]

df1[ , semesters_enrolled := mapvalues(df1$cohort, 
                                from = c(0, 1, 2, 3, 4), 
                                to = c(5, 4, 3, 2, 1))]

df1[ , .(count = .N), by=.(cohort_name)]
```


### EDA on variables

```{r}
table0 = df1[ ,.(count_group = .N, responsed = sum(response)), by = .(cohort_name, treatment_group_name)]
table0[ , rr := responsed/count_group]
table0
```

```{r}
table01 = df1[ ,.(count_group = .N, response = sum(response)), by = .(treatment_group_name, in_PST)]
table01[ , rr := response/count_group]
table01
```

> `No Incentive (Control)` and `$100 Lottery` treatment share the same number of observations who are in_PST, so no covariate balance check is needed. However, `No Incentive (Control)` and `$5 Incentive` treatment differ in the number of observations who are in_PST, so a covariate balance check is needed.

```{r warning=FALSE}
lr_PST_covBal <- df1[treatment_group %in% c(0, 1), lm(in_PST ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)'))]

stargazer(
  lr_PST_covBal,
  type = 'text',
  title = "Covariate Balance Check on PST:  No Incentive vs. 5 Per Survey Incentive",
  se = list(robust_SE(lr_PST_covBal)),
  header=F,
  covariate.labels = c("5 Dollar Incentive", "Baseline")
  )


```

> Randomization was successful because the covariate balance check reveals that the proportion of observations `in_PST` does not differ statistically significantly between control and the `$5 Incentive` treatment.


```{r}
table1 = df1[ ,.(count_group = .N, response = sum(response)), by = .(treatment_group_name)]
table1[ , response_rate := response/count_group]
table1
```


```{r}
table2 = df1[ ,.(count_group = .N, responsed = sum(response)), by = .(cohort_name, treatment_group_name, in_PST)]
table2[ , rr := responsed/count_group]
table2
```

### Regression Tables

#### Between No Incentive vs. $5 Incentive

```{r message=FALSE, warning=FALSE}
#Group 0 vs. Group 1
df01 <- df1[treatment_group %in% c(0,1)] # data that is only in control or treatment 1
lr1 <- df01[ , lm(response ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)'))]
lr2 <- df01[ , lm(response ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)') 
                  + relevel(factor(cohort_name), ref='Summer 2020'))]
lr3 <- df01[ , lm(response ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)') + in_PST)]
lr4 <- df01[ , lm(response ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)') + in_PST 
                  + relevel(factor(cohort_name), ref='Summer 2020'))]

stargazer(
  lr1, lr2, lr3, lr4,
  type = 'text',
  title = "Table 1: Linear Regression - No Incentive vs. $5 Per Survey Incentive",
  column.labels = c('Simple', 'Cohort Included', 'PST included', 'Cohort and PST included'),
  se = list(robust_SE(lr1), robust_SE(lr2), robust_SE(lr3), robust_SE(lr4)),
  header=F,
  notes = "Note: Uses Robust Standard Errors.",
  dep.var.labels = c("Response Rate"),
  add.lines = list(c("Cohort fixed effects", "No", "Yes", "No", "Yes"), c("PST fixed effects", "No", "No", "Yes", "Yes"),
                   c("Baseline is:", "5 dollar.", "5 dollar, Summer 2020.", "5 dollar, Not PST.", "5 dollar, Summer 2020, Not PST.")),
  covariate.labels = c("5 Dollar Incentive", "Fall 2020", 
                       "Fall 2021", "Spring 2021", 
                       "Summer 2021", 
                       "In PST", "Baseline")
  )
```

```{r}
tt01 <- df01[ , t.test(response~treatment_group_name)]
tt01
```

#### Between No Incentive vs $100 Lottery

```{r message=FALSE, warning=FALSE}
df02 <- df1[treatment_group %in% c(0,2)] # data that is in control or treatment2
lr02 <- df02[ , lm(response ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)'))]
lr02_a <- df02[ , lm(response ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)') 
                  + relevel(factor(cohort_name), ref='Summer 2020'))]
lr02_b <- df02[ , lm(response ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)') + in_PST)]
lr02_c <- df02[ , lm(response ~ relevel(factor(treatment_group_name), ref='No Incentive (Control)') + in_PST 
                  + relevel(factor(cohort_name), ref='Summer 2020'))]

stargazer(
  lr02, lr02_a, lr02_b, lr02_c,
  title = "Table 2: Linear Regression - No Incentive vs. $100 Lottery Win",
  column.labels = c('Simple', 'Cohort Included', 'PST included', 'Cohort and PST Included'),
  type = 'text',
  se = list(robust_SE(lr02), robust_SE(lr02_a), robust_SE(lr02_b), robust_SE(lr02_c)),
  notes = 'Note: Uses Robust Standard Error.',
  dep.var.labels = c("Response Rate"),
  add.lines = list(c("Cohort fixed effects", "No", "Yes", "No", "Yes"), c("PST fixed effects", "No", "No", "Yes", "Yes"),
                   c("Baseline is:", "5 dollar.", "5 dollar, Summer 2020.", "5 dollar, Not PST.", "5 dollar, Summer 2020, Not PST.")),
  covariate.labels = c("100 Dollar Lottery Incentive", "Fall 2020", 
                       "Fall 2021", "Spring 2021", 
                       "Summer 2021", 
                       "In PST", "Baseline")
)
```





```{r}
tt02 <- df02[ , t.test(response~treatment_group_name)]
tt02
```


#### Between $5 Incentive vs $100 Lottery

```{r message=FALSE, warning=FALSE}
df12 <- df1[treatment_group %in% c(1,2)] # data that is in treatment1 or treatment2
lr12 <- df12[ , lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive'))]
lr12_a <- df12[ , lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive') 
                  + relevel(factor(cohort_name), ref='Summer 2020'))]
lr12_b <- df12[ , lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive') + in_PST)]
lr12_c <- df12[ , lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive') + in_PST 
                  + relevel(factor(cohort_name), ref='Summer 2020'))]

stargazer(
  lr12, lr12_a, lr12_b, lr12_c,
  title = "Table 3: Linear Regression - $5 Per Survey Incentive vs. $100 Lottery Win",
  column.labels = c('Simple', 'Cohort Included', 'PST included', 'Cohort and PST Included'),
  type = 'text',
  se = list(robust_SE(lr12), robust_SE(lr12_a), robust_SE(lr12_b), robust_SE(lr12_c)),
  notes = 'Note: Uses Robust Standard Error.',
  dep.var.labels = c("Response Rate"),
  add.lines = list(c("Cohort fixed effects", "No", "Yes", "No", "Yes"), c("PST fixed effects", "No", "No", "Yes", "Yes"),
                   c("Baseline is:", "5 dollar.", "5 dollar, Summer 2020.", "5 dollar, Not PST.", "5 dollar, Summer 2020, Not PST.")),
  covariate.labels = c("100 Dollar Lottery Incentive", "Fall 2020", 
                       "Fall 2021", "Spring 2021", 
                       "Summer 2021", 
                       "In PST", "Baseline")
)
```





```{r}
tt12 <- df12[ , t.test(response~treatment_group_name)]
tt12
```



### Big Regression Tables


```{r message=FALSE, warning=FALSE}
lrt1 <- df1[ , lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive'))]

lrt2 <- df1[ , lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive') 
                  + relevel(factor(cohort_name), ref='Summer 2020'))]
lrt3 <- df1[ , lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive') 
                  + in_PST)]

lrt4 <- df1[ , lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive') 
                  + in_PST + relevel(factor(cohort_name), ref='Summer 2020'))]


stargazer(
  lrt1, lrt2, lrt3, lrt4,
  title = "Table 4: Linear Regression - Including All Treatments",
  column.labels = c('Simple', 'Cohort Included', 'PST Included', 'Cohort and PST Included'),
  type = 'text',
  se = list(robust_SE(lrt1), robust_SE(lrt2), robust_SE(lrt3), robust_SE(lrt4)),
  notes = 'Note: Uses Robust Standard Error.',
  dep.var.labels = c("Response Rate"),
  add.lines = list(c("Cohort fixed effects", "No", "Yes", "No", "Yes"), 
                   c("PST fixed effects", "No", "No", "Yes", "Yes"),
                   c("Baseline is:", "5 dollar.", "5 dollar, Summer 2020.", "5 dollar, Not PST.", "5 dollar, Summer 2020, Not PST.")),
  covariate.labels = c("100 Dollar Lottery Incentive", "No Incentive", "Fall 2020", 
                       "Fall 2021", "Spring 2021", 
                       "Summer 2021", 
                       "In PST", "Baseline")
)
```


## DONT ADD BELOW TABLES

> WARNING: POWER might be too low fpr HTE analysis b/c few samples. Maybe leave off.

```{r warning=FALSE}
# Heterogeneous Treatment Effects: in_PST 


lr_notPST <- df1[ in_PST %in% c(0), lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive'))]

lr_PST <- df1[ in_PST %in% c(1), lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive'))]

lr_notPST_cohort <- df1[ in_PST %in% c(0), lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive') + relevel(factor(cohort_name), ref='Summer 2020'))]

lr_PST_cohort <- df1[ in_PST %in% c(1), lm(response ~ relevel(factor(treatment_group_name), ref='$5 Incentive') + relevel(factor(cohort_name), ref='Summer 2020'))]

stargazer(
  lr_notPST, lr_PST, lr_notPST_cohort, lr_PST_cohort,
  title = "Table 4: Linear Regression - Heterogeneous Treatment Effects for being in PST",
  column.labels = c('Not PST', 'PST', 'Not PST, Cohorts', 'PST, Cohorts'),
  type = 'text',
  se = list(robust_SE(lr_notPST), robust_SE(lr_PST), robust_SE(lr_notPST_cohort), robust_SE(lr_PST_cohort)),
  notes = 'Note: Uses Robust Standard Error.',
  dep.var.labels = c("Response Rate"),
  add.lines = list(c("Cohort fixed effects", "No", "No", "Yes", "Yes"), 
                   c("Baseline is:", "5 dollar.", "5 dollar.", "5 dollar, Summer 2020.", "5 dollar, Summer 2020.")),
  covariate.labels = c("100 Dollar Lottery Incentive", "No Incentive", "Fall 2020", 
                       "Fall 2021", "Spring 2021", 
                       "Summer 2021", "Baseline")
)

```


### OLD CODE - NOT WORKING PROPERLY

```{r}
#df1[ , treatment_group_name := ifelse(treatment_group == 0, "No Incentive", ifelse(treatment_group == 1, "$5 Incentive", "$100 Lottery"))]
lrtotal1 <- df1[ , lm(response ~ relevel(factor(treatment_group), ref=2))]
#names(lrtotal1$coefficients) <- c('5_Incentive','No_Incentive','100_Lottery')
lrtotal2 <- df12[ , lm(response ~ relevel(factor(treatment_group), ref=1) + factor(cohort))]
#names(lrtotal2$coefficients) <- c('5_Incentive','No_Incentive','100_Lottery', 'Cohort1', 'Cohort2', 'Cohort3')
#lr12_b <- df12[ , lm(response ~ as.factor(treatment_group) + in_PST + factor(cohort))]

stargazer(
  lrtotal1, lrtotal2,
  title = "Table 2: Linear Regression - $5 Per survey incentive vs. $100 Lottery win",
  column.labels = c('Simple', 'Cohort Included', 'Cohort and PST'),
  type = 'text',
  #se = list(robust_SE(lr12), robust_SE(lr12_a), robust_SE(lr12_b)),
  se = list(robust_SE(lrtotal1), robust_SE(lrtotal2)),
  omit = 'cohort',
  notes = 'Note: Uses Robust Standard Error, Cohort included but ommitted in Model 2 and 3.'
)
```







